%-------------------------
% Resume in LaTeX (Based on Sourabh Bajaj Template)
% Avinash Mishra
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small#2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  {\Large \textbf{Avinash Mishra}} & Email: \href{mailto:avvin@hotmail.com}{avvin@hotmail.com}\\
  \href{https://www.linkedin.com/in/mishav9}{linkedin.com/in/mishav9} & Mobile: \href{tel:+919381292195}{+91-93812-92195} \\
   & Hyderabad, Telangana, 500089 \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Professional Summary}
Results-driven Data Engineer with 6+ years of experience designing and optimizing data pipelines, enhancing deployment efficiency through DevOps practices, and transforming complex data sets into actionable insights. Consistently delivered 30\% improvement in pipeline performance and reduced data processing time by 40\%. Managed ETL processes handling over 100+ TB of data daily across cloud and on-prem platforms. Led cross-functional team, driving innovation and supporting data-driven strategies in product-based environments, particularly in telecom and healthcare domains. Implemented automation solutions resulting in a 25\% reduction in manual data management tasks.

%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Verizon}{Hyderabad, India}
{Member Technical Staff-III | Team: Delivery Accelerators}{2023 -- Present}
\resumeItemListStart
\item Spearheaded design and establishment of scalable CI/CD pipelines, reducing deployment time by 30\%.
\item Migrated 50+ applications to containerized environments, improving resource utilization by 40\%.
\item Engineered a robust security framework for artifact management, reducing vulnerabilities by 65\%.
\item Pioneered Infrastructure as Code (IaC) practices, accelerating environment provisioning by 70\%.
\resumeItemListEnd

\resumeSubheading
{Verizon}{Hyderabad, India}
{Member Technical Staff-II | Team: Intelligent Edge Network (IEN)}{2021 -- 2023}
\resumeItemListStart
\item Architected real-time data ingestion system for network feeds, boosting data processing speed by 45\%.
\item Fine-tuned batch and streaming flow, achieving 35\% improvement in overall performance.
\item Developed an AI-driven alarm management system, reducing false positives by 60\%.
\item Orchestrated migration of critical systems from Yahoo private cloud to GCP, achieving 99.99\% uptime.
\resumeItemListEnd

\resumeSubheading
{Verizon}{Hyderabad, India}
{Analyst - System Development | Team: Network Performance Intelligence (NPI)}{2019 -- 2021}
\resumeItemListStart
\item Engineered automated server maintenance scripts, reducing manual intervention by 75\%.
\item Replaced OBIEE reports with Python automation, cutting processing time by 50\%.
\item Implemented Apache NiFi for secure file transfers, reducing transfer errors by 90\%.
\item Enhanced Pig Latin/Hive scripts, improving query performance by 40\%.
\resumeItemListEnd

\resumeSubheading
{Accenture}{Hyderabad, India}
{Application Developer Analyst | Major Healthcare Client}{2017 -- 2019}
\resumeItemListStart
\item Created and maintained Informatica workflows to refresh data marts from Oracle EBS to Teradata.
\item Increased ETL performance by resolving bottlenecks and improving job reliability.
\item Collaborated with stakeholders to address data issues aligned with business requirements.
\resumeItemListEnd

\resumeSubSubheading{Leading Telecom Client}{}
\resumeItemListStart
\item Utilized OBIEE dashboards for visualization, providing actionable insights.
\item Developed and maintained ETL processes ensuring data accuracy and consistency.
\item Improved ETL efficiency by optimizing schedules and automating tasks.
\item Developed optimized Pig Latin/Hive scripts improving query performance by 40\%.
\item \textbf{Tech Stack:} Informatica PowerCenter, Shell Scripting, SQL, Oracle Exadata.
\resumeItemListEnd

\resumeSubheading
{Accenture}{Hyderabad, India}
{Application Developer Associate}{2016 -- 2017}
\resumeItemListStart
\item Boosted production support processes by adding support documentation.
\item Established automated email notification system improving team communication.
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Kalinga University}{Odisha, India}
{Bachelor of Technology in Electrical and Electronics Engineering}{2011 -- 2015}
\resumeSubHeadingListEnd

%-----------TECHNICAL PROFICIENCIES---------------
\section{Technical Proficiencies}
\resumeItemListStart
\item \textbf{Cloud \& DevOps:} GCP, AWS, Yahoo Private Cloud, Docker, Kubernetes, Jenkins, Ansible, Terraform, GitLab-CI
\item \textbf{Programming:} Python, Java, Scala, Shell Scripting
\item \textbf{Big Data \& Analytics:} Apache Spark, Dataflow, Storm, Hive, Oozie, Airflow, SQL
\item \textbf{ETL \& Reporting:} Informatica PowerCenter, OBIEE, Ab Initio
\resumeItemListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\resumeItemListStart
\item Google Professional Data Engineer (2024)
\item SAFe 5 Practitioner
\resumeItemListEnd

%-----------AWARDS-----------------
\section{Awards \& Recognition}
\resumeItemListStart
\item Verizon Spotlight Award (2020, 2022, 2024) for exceptional contributions to critical projects.
\item Star Performer (2018) for outstanding performance and innovation.
\resumeItemListEnd

\end{document}
